---
title: "ingest"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, message = F, warning = F)
```

## TODO

1. PROBLEM. Data is too big for simple interactive time-series plot (ie dygraphs) if on same Rmd output html page. The folder of *.csv's [robomusseldata20201030 - Google Drive](https://drive.google.com/drive/u/3/folders/1kzjZ72vFxRGsafTgCCzq6cXIhQ1GYQa3) contains 317 files totalling 236 MB. SOLUTION(s):
    1. Read into SQLite database and show as Shiny app.


## Ingest single txt

```{r}
# libraries
if (!require(librarian)){
  install.packages("librarian")
  library(librarian)
}
shelf(
  # time-series
  caTools, tools, dygraphs, xts, leaflet,
  # tidyverse
  fs, glue, lubridate, tidyverse)

# paths & variables
user <- Sys.info()[["user"]]
# set dir_data as filepath for robomussels data 
dir_data <- case_when(
  #user == "bbest"       ~ "/Users/bbest/Downloads/robomusseldata20201030",
  user == "bbest"       ~ "/Volumes/GoogleDrive/My Drive/projects/mbon-p2p/data/rocky/MARINe/robomusseldata20201030",
  user == "cdobbelaere" ~ "/Users/cdobbelaere/Documents/robomussels/robomusseldata20201030")
dir_avg <- file.path(dirname(dir_data), "robomusseldata20201030_avg")
stopifnot(any(dir.exists(c(dir_data, dir_avg))))

# TODO: iterate over files in dir_data

# path individual tab-seperated value (*.tsv) file
tsv              <- file.path(dir_data, "BMRMUSCABD3_2012.txt")
csv_hourlymean   <- glue("{dir_avg}/{basename(path_ext_remove(tsv))}_hourlymean.csv")
csv_movingwindow <- glue("{dir_avg}/{basename(path_ext_remove(tsv))}_movingwindow.csv")
csv_dailyavg     <- glue("{dir_avg}/{basename(path_ext_remove(tsv))}_dailyavg.csv")

stopifnot(file.exists(tsv))

# read data from individual tsv files
d <- read_tsv(tsv) %>% 
  mutate(
    time = parse_date_time(Time_GMT, "m/d/y H:M")) %>% # parse through datetimes, store as time col.
  select(-Time_GMT) %>% # get rid of original time column
  arrange(time) # d # sort by ascending time 

# convert to eXtensible Time Series for dygraph
x <- d 
x <- xts(select(x, -time), order.by=x$time) # select only Temp_C and order by time, store as xts object 

# output dygraph interactive plot
dygraph(x, main="Temp_C") %>%
  dyOptions(
    colors = "red",
    fillGraph = TRUE, fillAlpha = 0.4) %>% 
  dyRangeSelector()
```

# Smoothing

## 1. Hourly mean (from every 10 min)

```{r}
# create df containing hourly mean temp data
d_hourlymean <- d %>% 
  mutate(time = floor_date(time, unit = "hour")) %>% # round each time down to the nearest hourly boundary 
  # (could alternatively round up with ceiling_date() or round to nearest values with round_date())
  group_by(time) %>% # group by hour
  summarize(Temp_C_hourly_mean = mean(Temp_C)) # calculate mean for each hour

# show file size difference from original
write_csv(d_hourlymean, csv_hourlymean)
file_size(c(tsv, csv_hourlymean))

# convert to xts for dygraph
x_hourlymean <- d_hourlymean
x_hourlymean <- xts(select(x_hourlymean, -time), order.by=x_hourlymean$time) 

# output dygraph interactive plot
dygraph(x_hourlymean, main="Hourly_Mean_Temp_C") %>%
  dyOptions(
    colors = "red",
    fillGraph = TRUE, fillAlpha = 0.4) %>% 
  dyRangeSelector()
```

## 2. Min/max over 6 hr moving window
(note: can do rolling averages directly in dygraphs too with dygraph() %>% dyRoller(rollPeriod = 6)

```{r}
# 6 hour moving average, using hourly averages from earlier
d_movingwindow <- d_hourlymean %>% 
  mutate(
    # min for 6 hr moving window, based on hourly mean
    Temp_C_min_06_hours  = runmin(Temp_C_hourly_mean,  k=6, alg="C", endrule="constant", align="center"),
    # mean for 6 hr moving window, based on hourly mean
    Temp_C_mean_06_hours = runmean(Temp_C_hourly_mean, k=6, alg="C", endrule="constant", align="center"),
    # max for 6 hr moving window, based on hourly mean
    Temp_C_max_06_hours  = runmax(Temp_C_hourly_mean,  k=6, alg="C", endrule="constant", align="center")
    ) %>% 
  select(-Temp_C_hourly_mean)
  
# show file size difference from original
write_csv(d_movingwindow, csv_movingwindow)
file_size(c(tsv, csv_movingwindow))

# convert to xts  
x_movingwindow <- xts(select(d_movingwindow, -time), order.by=d_movingwindow$time) 

# output dygraph plot
dygraph(x_movingwindow, main="Temp_C") %>%
  dySeries(
    c("Temp_C_min_06_hours",
      "Temp_C_mean_06_hours",
      "Temp_C_max_06_hours"),
    label = "Temp (ºC) over 6 hour moving window",
    color = "orangered") %>% 
  dyOptions(
    #colors = c("orange", "orangered", "red"),
    fillGraph = FALSE, fillAlpha = 0.4) %>% 
  dyRangeSelector() 

# is there a way to display min/max data labels when using min/max as upper/lower bars?
```

```{r}
# alternative: moving min and max using original 
# but this doesn't reduce amount of data so not ideal
d_movingwindow_orig <- d %>% 
  mutate(time = floor_date(time, unit = "hour")) %>% 
  mutate(
    Temp_C_min_06_hours  = runmin(Temp_C,  k=6, alg="C", endrule="constant", align="center"),
    Temp_C_max_06_hours  = runmax(Temp_C,  k=6, alg="C", endrule="constant", align="center"),
    Temp_C_mean_06_hours = runmean(Temp_C, k=6, alg="C", endrule="constant", align="center")
    ) %>% 
  select(-Temp_C)
  #group_by(time) %>% 
  #mutate(Temp_C_hourly_mean = mean(Temp_C)) %>% 
  #ungroup()

x_movingwindow_orig <- xts(select(d_movingwindow_orig, -time), order.by=d_movingwindow_orig$time) # View(x_movingwindow_orig)

# output dygraph interactive plot
# ideally would like to plot the means with fill but plot the mins and maxes just with line
dygraph(x_movingwindow_orig, main="Temp_C") %>%
  dySeries(
    c("Temp_C_min_06_hours",
      "Temp_C_mean_06_hours",
      "Temp_C_max_06_hours"),
    label = "Temp (ºC) over 6 hour moving window",
    color = "orangered") %>% 
  dyOptions(
    #colors = c("orange", "orangered", "red"),
    fillGraph = TRUE, fillAlpha = 0.4) %>% 
  dyRangeSelector() 

```

## 3. Min/max over day

First find points of inflection to break up day. Possibly averaging around 3 points of max in case anomalous 

```{r}
d_dailyavg <- d %>% 
  mutate(
    day = floor_date(time, unit = "day")) %>%
  group_by(day) %>%
  summarize(
    temp_c_avg = mean(Temp_C),
    temp_c_min = min(Temp_C),
    temp_c_max = max(Temp_C))

# show file size difference from original
write_csv(d_dailyavg, csv_dailyavg)
file_size(c(tsv, csv_dailyavg))

# convert to xts for dygraph
x_dailyavg <- d_dailyavg
x_dailyavg <- xts(select(x_dailyavg, -day), order.by=x_dailyavg$day) 

dygraph(x_dailyavg, main="Daily Temperature (ºC)") %>%
  dySeries(
    c("temp_c_min",
      "temp_c_avg",
      "temp_c_max"),
    label = "Daily Temperature (ºC)",
    color = "orangered") %>% 
  dyOptions(
    fillGraph = FALSE, fillAlpha = 0.4) %>%
  dyRangeSelector() 
```

# Sorting zones and locations

## Combine metadata for each site

```{r}
# read metadata
robo_reference <- read_csv("ben_best_roboreference20201030.csv") 
robo_metadata  <- read_csv("Robomussel metadata.csv") %>% 
  rename(
    microsite_id   = `microsite id`,
    logger_type    = `logger type`,
    tidal_height_m = `tidal height (m)`,
    wave_exposure  = `wave exposure`,
    start_date     = `start date`,
    end_date       = `end date`
    )

robo_files <- list.files(path = dir_data, pattern = "*.txt", full.names = TRUE)

loggerID <- rep(NA, length.out = length(robo_files))

# keep only logger name from each file's name
for (i in 1:length(robo_files)){
  loggerID[i] <- sub("\\_.*", "", basename(file_path_sans_ext(robo_files[i])))
  }

# copy all info from robo_metadata into dataframe
robo_list <- tibble(loggerID) 
robo_list <- 
  semi_join(
    x = robo_metadata, y = robo_list,
    by = c("microsite_id" = "loggerID")) %>% 
  left_join(
    y = robo_reference,
    by = c("site" = "robo_location"),
    keep = FALSE ) %>%
  group_by(site) %>% 
  mutate(loggers_per_site = n()) %>% 
  ungroup() %>% 
  # remove duplicate columns
  # (latitude = robo_latitude, longitude = robo_longitude, location = marine_site_name)
  select(
    -latitude, -longitude, -marine_site_name) 

```

## Location (map of all locations & zones)

### Label styles and color palettes

```{r}
label_style_normal <- list(
  "color"        =  "black",
  "font-family"  =  "default",
  "box-shadow"   =  "3px 3px rgba(0,0,0,0.25)",
  "font-size"    =  "11px",
  "border-color" =  "rgba(0,0,0,0.5)"
)
  
label_style_bold <- list(
  "color"        =  "black",
  "font-family"  =  "default",
  "font-weight"  =  "bold",
  "box-shadow"   =  "3px 3px rgba(0,0,0,0.25)",
  "font-size"    =  "15px",
  "border-color" =  "rgba(0,0,0,0.5)"
  )

label_style_sites <-list(
  "color"        =  "white",
  "font-style"   =  "italic",
  "font-family"  =  "default",
  "font-size"    =  "12px"
  )

# Discrete color palette by site
pal_sites <- colorFactor(
  palette = "Dark2",
  domain = robo_list$location
  )

pal_zones <- colorFactor(
  palette = "YlOrBr",
  domain = robo_list$zone
  )
```

### Map of all sites

```{r}
# good but problem: only plotting one logger per site if multiple loggers with 
# same robo_longtitude and robo_latitude 
# solution: Marker Clusters

# would be cool to find spatial data (polygons) for each site to make outline using that instead of with rectangles
# also would like to map temp data

sites_map <- leaflet(data = robo_list) %>% 
  addProviderTiles(
    providers$Esri.WorldImagery,
    providerTileOptions(detectRetina = T)
    ) %>% 
  addMarkers(
    lat = ~robo_latitude,
    lng = ~robo_longitude,
    group = "Loggers", 
    label = ~microsite_id,
    clusterOptions = markerClusterOptions(),
    labelOptions = labelOptions(
      direction = "bottom",
      offset = c(2,2), sticky = T,
      style = label_style_normal
      ),
    popup = paste0(
      "Logger: ", robo_list$microsite_id, "<br>",
      "Zone: ", robo_list$zone, "<br>",
      robo_list$location, ", ", robo_list$region, "<br>",
      "(", robo_list$robo_latitude, "ºN, ",
      robo_list$robo_longitude, " ºW)", sep = "", "<br>"
      ),
    popupOptions = popupOptions(
      maxWidth = 300, minWidth = 50, maxHeight = NULL,
      autoPan = T, keepInView = F, closeButton = T
      )
    ) %>%
  addLabelOnlyMarkers(
    lat = ~marine_latitude, lng = ~marine_longitude,
    label = ~location,
    group = "Sites",
    labelOptions = labelOptions(
      direction = "left",
      offset = c(-30,10), sticky = T,
      noHide = T, textOnly = T,
      style = label_style_sites
      )
    ) %>% 
  addRectangles(
    lat1 = (~marine_latitude - .5), lat2 = (~marine_latitude + .5),
    lng1 = (~marine_longitude - .5), lng2 = (~marine_longitude + .5),
    label = ~location,
    fillColor = "transparent",
    group = "Sites",
    fillOpacity = 0.5, color = ~pal_sites(location),
    labelOptions = labelOptions(
      direction = "left",
      offset = c(-30,10), sticky = T,
      noHide = F, 
      style = label_style_bold
      )
    ) %>% 
  setView(
    lat = mean(robo_list$robo_latitude),
    lng = mean(robo_list$robo_longitude), 
    zoom = 7) %>%
  addEasyButton(
    easyButton(
      icon="fa-globe",
      title="Zoom out to level 1",
      onClick=JS("function(btn, map){ map.setZoom(1); }")
      )
    ) %>% 
  addLegend(
    position = "bottomright", opacity = 0.8,
    pal = pal_sites, values = ~location,
    group = "Sites",
    title = "Site"
    ) %>% 
  addMiniMap(
    position = "topright",
    tiles = providers$Esri.WorldImagery,
    toggleDisplay = T, 
    height = 70, width = 70
    ) %>% 
  addLayersControl(
    overlayGroups = c("Loggers", "Sites"),
    options = layersControlOptions(collapsed = FALSE)
    )

sites_map  

```

### Map of individual logger

### ideally want to work on customizing marker colors according to zone

```{r}
# filter out data for each individual logger
for (i in 1:nrow(robo_list)) {
  robo_list_i <- robo_list[i,]
  assign(paste0("robo_list_", i), robo_list_i)
}

# one individual logger map (logger 11)
indiv_logger_map <- leaflet(data = robo_list_11) %>% 
  addProviderTiles(
    providers$Esri.WorldImagery,
    providerTileOptions(detectRetina = T)
    ) %>% 
  addMarkers(
    lat = ~robo_latitude,
    lng = ~robo_longitude,
    group = "Loggers", 
    label = ~microsite_id,
    labelOptions = labelOptions(
      direction = "bottom",
      offset = c(2,2), sticky = T,
      style = label_style_normal
      ),
    popup = paste0(
      "Logger: ", robo_list_11$microsite_id, "<br>",
      "Zone: ", robo_list_11$zone, "<br>",
      robo_list_11$location, ", ", robo_list_11$region, "<br>",
      "(", robo_list_11$robo_latitude, "ºN, ",
      robo_list_11$robo_longitude, " ºW)", sep = "", "<br>"
      ),
    popupOptions = popupOptions(
      maxWidth = 300, minWidth = 50, maxHeight = NULL,
      autoPan = T, keepInView = F, closeButton = T
      )
    ) %>%
  addLabelOnlyMarkers(
    lat = ~marine_latitude, lng = ~marine_longitude,
    label = ~location,
    group = "Sites",
    labelOptions = labelOptions(
      direction = "left",
      offset = c(-30,10), sticky = T,
      noHide = T, textOnly = T,
      style = label_style_sites
      )
    ) %>% 
  addRectangles(
    lat1 = (~marine_latitude - .5), lat2 = (~marine_latitude + .5),
    lng1 = (~marine_longitude - .5), lng2 = (~marine_longitude + .5),
    label = ~location,
    fillColor = "transparent",
    group = "Sites",
    fillOpacity = 0.5, color = ~pal_sites(location),
    labelOptions = labelOptions(
      direction = "left",
      offset = c(-30,10), sticky = T,
      noHide = F, 
      style = label_style_bold
      )
    ) %>% 
  setView(
    lat = mean(robo_list_11$robo_latitude),
    lng = mean(robo_list_11$robo_longitude), 
    zoom = 7) %>%
  addEasyButton(
    easyButton(
      icon="fa-globe",
      title="Zoom out to level 1",
      onClick=JS("function(btn, map){ map.setZoom(1); }")
      )
    ) %>% 
  addLegend(
    position = "bottomright", opacity = 0.8,
    pal = pal_sites, values = ~location,
    group = "Sites",
    title = "Site"
    ) %>% 
  addMiniMap(
    position = "topright",
    tiles = providers$Esri.WorldImagery,
    toggleDisplay = T, 
    height = 70, width = 70
    ) %>% 
  addLayersControl(
    overlayGroups = c("Loggers", "Sites"),
    options = layersControlOptions(collapsed = FALSE)
    )

indiv_logger_map


```


```{r}
# create logger maps for every individual logger

for (i in 1:nrow(robo_list)) {
  
  robo_list_i <- robo_list[i,]
  
  indiv_logger_map_i <- leaflet(data = robo_list_i) %>% 
    addProviderTiles(
      providers$Esri.WorldImagery,
      providerTileOptions(detectRetina = T)
      ) %>% 
    addMarkers(
      lat = ~robo_latitude,
      lng = ~robo_longitude,
      group = "Loggers", 
      label = ~microsite_id,
      labelOptions = labelOptions(
        direction = "bottom",
        offset = c(2,2), sticky = T,
        style = label_style_normal
        ),
      popup = paste0(
        "Logger: ", robo_list_i$microsite_id, "<br>",
        "Zone: ", robo_list_i$zone, "<br>",
        robo_list_i$location, ", ", robo_list_i$region, "<br>",
        "(", robo_list_i$robo_latitude, "ºN, ",
        robo_list_i$robo_longitude, " ºW)", sep = "", "<br>"
        ),
      popupOptions = popupOptions(
        maxWidth = 300, minWidth = 50, maxHeight = NULL,
        autoPan = T, keepInView = F, closeButton = T
        )
      ) %>%
    addLabelOnlyMarkers(
      lat = ~marine_latitude, lng = ~marine_longitude,
      label = ~location,
      group = "Sites",
      labelOptions = labelOptions(
        direction = "left",
        offset = c(-30,10), sticky = T,
        noHide = T, textOnly = T,
        style = label_style_sites
        )
      ) %>% 
    addRectangles(
      lat1 = (~marine_latitude - .5), lat2 = (~marine_latitude + .5),
      lng1 = (~marine_longitude - .5), lng2 = (~marine_longitude + .5),
      label = ~location,
      fillColor = "transparent",
      group = "Sites",
      fillOpacity = 0.5, color = ~pal_sites(location),
      labelOptions = labelOptions(
        direction = "left",
        offset = c(-30,10), sticky = T,
        noHide = F, 
        style = label_style_bold
        )
      ) %>% 
    setView(
      lat = mean(robo_list_i$robo_latitude),
      lng = mean(robo_list_i$robo_longitude), 
      zoom = 7) %>%
    addEasyButton(
      easyButton(
        icon="fa-globe",
        title="Zoom out to level 1",
        onClick=JS("function(btn, map){ map.setZoom(1); }")
        )
      ) %>% 
    addLegend(
      position = "bottomright", opacity = 0.8,
      pal = pal_sites, values = ~location,
      group = "Sites",
      title = "Site"
      ) %>% 
    addMiniMap(
      position = "topright",
      tiles = providers$Esri.WorldImagery,
      toggleDisplay = T, 
      height = 70, width = 70
      ) %>% 
    addLayersControl(
      overlayGroups = c("Loggers", "Sites"),
      options = layersControlOptions(collapsed = FALSE)
    )
  
  assign(paste0("indiv_logger_map_", i), indiv_logger_map_i)
  
}

# example
indiv_logger_map_10


```

